Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-20 code/plots.Rmd
added code for figs

>>>>

```{r}
all_sim |> 
    mutate(across(type, factor, levels = c("Opt const mortality", "80% opt const mortality", 
                                           "DRL"))) |>
    group_by(rep, type) |>
    filter(t==max(t), species=="X", rep < 10) |>
    ggplot(aes(rep,t)) + 
        geom_col()  + 
        facet_wrap(~type) + 
        labs(y = "episode length", x = "repetition") +
        theme(axis.text.x = element_blank())
```

### 2023-01-20 manuscript/manuscript.Rmd
added code for figs

header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{bookmark}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \linenumbers
  - \doublespacing

@@

@@

\begin{figure}
	\includegraphics[width=\linewidth]{Figures/timeseries.png}
\caption{
\label{fig:one timeseries}
tbd
}
\end{figure}

@@

>>>>

header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{bookmark}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \usepackage{caption}
  - \usepackage{subcaption}
  - \linenumbers
  - \doublespacing

@@

```{r}
library(tidyverse)
msy <- read_csv("../data/msy.csv.gz")
ppo <- read_csv("../data/ppo-200.csv")
escapement <- read_csv("../data/escapement.csv.gz", show_col_types = FALSE)

# rename some columns for figure purposes:
colnames(msy) <- c('t', 'rep', 'action', 'reward', 'X', 'Y', 'Z')
colnames(ppo) <- c('1', 't', 'X', 'Y', 'Z', 'action', 'reward', 'rep')

# ppo dataset uses step rewards rather than cumulative rewards, which is what is useful here.
# so, switch stuff around:
ppo |> 
    group_by(rep) |> 
    mutate(cumulative_reward = cumsum(reward)) |>
    within(rm("reward", "1")) |>
    rename(reward = cumulative_reward)

# set up for plots:

# best constant effort based on the data on ../data/msy.csv.gz
best_action <- 0.0465
msy_sim <- msy |>
    filter(action == best_action) |> 
    group_by(rep) |>
    pivot_longer(c("X", "Y", "Z"),
                names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1, policy = "msy") # natural units, policy name

i <- which.min(abs(actions - best$action* 0.8))
tac_sim <- msy |> 
    filter(action == actions[[i]]) |>
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1, policy = "tac")

ppo_sim <- ppo |> 
    mutate(escapement = (X+1) - action * (X+1),
        effort = action) |>
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(policy = "ppo") # already in natural units

best_e <- 0.62 # optimal constant escapement, computed from ../data/escapement.csv.gz
esc_sim <- escapement |> 
    rename(escapement = action) |>
    filter(escapement == best_e) |> # data had a naming problem
    pivot_longer(c("X", "Y", "Z"),
        names_to = "species", values_to = "abundance") |>
    mutate(abundance = abundance + 1)
```

@@

```{r fig.cap="TBD."}

```

\begin{figure}
	\includegraphics[width=\linewidth, height = 0.2\textheight]{Figures/timeseries.png}
\caption{
\label{fig:one timeseries}
tbd
}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\linewidth]{Figures/ep_length.png}
        \caption{Episode lengths}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\linewidth]{Figures/rewards.png}
        \caption{Episode rewards}
    \end{subfigure}
    \caption{
        TBD
    }
    \label{fig:lengths and rewards}
\end{figure}
